---
title: "Using with htmlwidgets"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using with htmlwidgets}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = FALSE
)
```

```{r setup}
library(snapper)
library(shiny)
library(leaflet)
```

`snapper` can be used to capture more complex elements in an app such as leaflet htmlwidgets.

The user must set the correct `html2canvas` configuration:

```{r}
snapper::config(
  allowTaint = TRUE,
  useCORS = TRUE
)
```

For more configurations see `snapper::config`.

## Basic

```{r}
shiny::runGadget(
  fluidPage(
    leafletOutput('myMap'),
    snapper::load_snapper(),
    snapper::preview_button(
      ui = '#myMap',
      opts = snapper::config(
        allowTaint = TRUE,
        useCORS = TRUE)
    ),
    snapper::snapper_div()
  ),
  server = function(input, output) {
    map = leaflet() %>%
      addTiles() %>%
      setView(-93.65, 42.0285, zoom = 17)
    output$myMap = renderLeaflet(map)
  },
  viewer = shiny::browserViewer()
)

```

## Advanced

The configurations can also be dependent on reactive elements in the app. 

In this examples the leaflet image is cropped as a function of the two sliderInput elements.


```{r}

shiny::runGadget(
  fluidPage(
    snapper::load_snapper(),
    sidebarLayout(
      sidebarPanel = sidebarPanel(
        sliderInput(
          inputId = 'x_slide',
          label = 'Crop X',
          min = 0,
          max = 1200,
          value = 555
        ),
        sliderInput(
          inputId = 'y_slide',
          label = 'Crop Y',
          min = 0,
          max = 400,
          value = 0
        ),
        uiOutput('mybtn')
      ),
      mainPanel = mainPanel(
        leafletOutput('myMap'),
        snapper::snapper_div()
      )
    )),
  server = function(input, output) {
    output$mybtn <- renderUI({
       snapper::preview_button(
        ui = '#myMap',
        opts = snapper::config(
          allowTaint = TRUE,
          useCORS = TRUE,
          x = as.numeric(input$x_slide),
          y = as.numeric(input$y_slide)
          )
      )
    })
    map = leaflet() %>%
      addTiles() %>%
      setView(-93.65, 42.0285, zoom = 17)
    output$myMap = renderLeaflet(map)
  },
  viewer = shiny::browserViewer()
)

```
